### 2013-12-03 manuscripts/reply/short-reply.tex
Working on reply ms.
Adding reference for dpp-msbayes manuscript to `references.bib`, moving
sections from `short-reply.tex` to `reply-si-main.tex`, and miscallenous
edits throughout `short-reply.tex`.

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    are affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citep{Huang2011} introduced an approximate Bayesian approach which can be
    used to estimate the probability of a model in which multiple sets of taxa
    diverge at the same time. 
    This method (implemented in the software \msb) does not require a common
    set of character data that links all of the taxa under investigation, but
    does require the relative mutation rates among the taxa and loci to be
    assumed a priori.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the 
    prior that is chosen and that the inference method had low power
    to detect variation in divergences times.
    These results were not surprising, in light of a rich statistical literature
    that shows that the marginal likelihood of a model is quite sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically informed uniform
    priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an 
    empirical Bayesian stance for this model-choice problem.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes}

@@

\citet{Oaks2012} suggest the primary cause of the bias of \msb is the low
marginal likelihoods of parameter-rich models integrated over vast parameter
space with low probability of producing the data, yet relatively high prior
density \citep{Lindley1957} imposed by the uniformly distributed prior on
divergence times.
Note, this is a statistical issue extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is the result of a numerical issue
intrinsic to \msb, concluding the method's rejection algorithm is inefficient
and will be biased toward models with fewer divergence-time parameters, because
the parameter space of these models are more densely sampled relative to models
with more divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results of additional analyses that, when combined with
the results of \citet{Oaks2012}, strongly suggest small marginal likelihoods of
models with more parameter space is a primary mechanism by which uniform priors
are causing the bias of \msb.

@@

% There are also differences between the papers regarding potential solutions to
% the bias.
\citet{Oaks2012} suggest alternative prior probability distributions on
divergence-times and other nuisance parameters could increase the marginal
likelihoods of models with more divergence-time parameters and thus reduce the
bias.
Alternatively, \citet{Hickerson2013} present an approach that uses empirically
informed priors and Bayesian model-averaging in an attempt to accommodate
uncertainty in selecting priors.
% \citet{Hickerson2013} champion this strategy as a means of avoiding the
% pitfalls raised by \citet{Oaks2012}.
In general, we agree with the use of Bayesian model averaging to obtain a
posterior estimate marginalized over uncertainty in prior choice.
However, we question whether adding an additional dimension of model choice
that samples over empirically informed uniform priors is a fruitful solution
for an already biased model-choice method.

In this paper, we discuss the potential theoretical and practical problems of
using empirically informed priors for Bayesian model choice.
Furthermore, we evaluate the empirical Bayesian model averaging approach of
\citet{Hickerson2013} as a potential solution to the biases revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different time units, which makes the results presented
in their response difficult to interpret (see Supporting Information for
details).
However, here we show that even when this error is avoided, the empirical
Bayesian model-averaging approach of \citet{Hickerson2013} remains biased
toward clustered divergence models, and is predisposed to excluding true
parameter space.
The approach provides another means by which the method can ``escape'' models
with large parameter space, and the method's bias toward smaller models
remains.
Importantly, this bias can manifest in the preference of models that exclude
from consideration the true values of the parameters.

@@

\citet{Hickerson2013} suggest that \citet{Oaks2012} should have used their
data to inform their prior on divergence times (i.e., an empirical Bayesian
approach).
However, \citet{Oaks2012} did use empirically informed priors to mimic
empirical situations in which a large amount of prior information is available;
they did so to assess the prior sensitivity of the method and to determine if
uniform priors in such situations are narrow enough to avoid the bias toward
models with few divergence events.
The results of \citet{Oaks2012} and \citet{Hickerson2013} showed the method is
highly sensitive to the prior on divergence times.
Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
divergences even under the informed priors.

@@

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a method of inductive learning in which Bayes' rule is
used to update our beliefs about a model $M$ as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values for model $M$, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta \given M)$ describes our belief that
any given \myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta, M)$ measures our belief that any dataset \alignment{}{}
will be generated by any state \myTheta{} of model $M$.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}, M) = \frac{p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M)}{p(\alignment{i}{} \given M)},
    \label{eq:bayesrule}
\end{equation}
where
\begin{equation}
    p(\alignment{i}{} \given M) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M) d\myTheta{}
    \label{eq:marginallikelhiood}
\end{equation}
is the marginal likelihood of the model.
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

Thus, empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and incorrectly shaped;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
This is not to say that empirical Bayesian approaches are not useful.
Empirical Bayes is a well-studied branch of Bayesian statistics that has given
rise to many inference methods that provide means of
parameter estimation that often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

@@

Another important difference of Bayesian model choice illustrated by
Equation~\ref{eq:bayesmodelchoice} is that the value of interest, the
posterior probability of a model, is not a function of \myTheta{}, because
it is integrated out of the marginal likelihoods of the candidate models.
Thus, unlike parameter estimates, the estimated posterior probability of a
model is a single value (rather than a distribution) lacking a measure of
posterior uncertainty.
Also, unlike model parameters, the posterior probabilities of candidate
models have no clear true values.
In some simple situations we might suspect that one model is correct and the
rest are wrong, but in most applications, we know that all the models under
consideration are oversimplifications of reality.
Thus, model posterior probabilities are inherently measures of our belief in
the models after our prior beliefs are updated by the data being analyzed.

@@

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the fairness of a particular coin, and we
denote the unknown probability of it landing heads as \myTheta{}.
More specifically, we are interested in the probability of two models, $M_1$
and $M_2$.
In both models the outcomes of flipping the coin are assumed to be binomially
distributed, but under $M_1$ the coin is weighted toward landing heads (i.e.,
$\myTheta{} > 0.5)$), whereas under $M_2$, the coin is weighted toward landing
tails (i.e., $\myTheta{} < 0.5$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times, and so we decide to use these data in specifying a
beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin $N=10$ times, $y=3$ of which land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$
(Figure~\ref{figCoinFlip}).
The maximum a posteriori (MAP) estimate of the probability of heads is 0.429,
and following Equation~\ref{eq:marginallikelhiood} the marginal likelihoods of
our models of interest are
\begin{equation}
    p(y=3, N=10 \given M_1) = \int_{0.5}^{1} p(y=3, N=10 \given
    \myTheta{}, M_1)p(\myTheta{} \given M_1) d\myTheta{} \approx 0.029,
\end{equation}
and
\begin{equation}
    p(y=3, N=10 \given M_2) = \int_{0}^{0.5} p(y=3, N=10 \given
    \myTheta{}, M_2)p(\myTheta{} \given M_2) d\myTheta{} \approx 0.097.
\end{equation}
Given the models have equal probability under our prior, and following
Equation~\ref{eq:bayesmodelchoice}, we can calculate the posterior
probability of Model 1 as
\begin{equation}
    p(M_1 \given y=3, N=10) = \frac{p(y=3, N=10 \given M_1)}{p(y=3, N=10 \given
    M_1) + p(y=3, N=10 \given M_2)} \approx 0.23.
\end{equation}
This is the correct posterior probability of Model 1 given our prior information
and data.

To give the data more weight relative to the prior, we could use it twice, and
calculate an empirical Bayes estimate using a prior of $beta(13,17)$.
This results in a distribution of $beta(16, 24)$ (Figure~\ref{figCoinFlip}),
with a MAP estimate of 0.395, and $p(M_1 \given y=3, N=10) = 0.10$.
The estimated posterior distribution of the parameter, and resulting MAP
estimate, is similar whether or not an empirically informed prior is used.
However, the posterior probability of Model 1 is very sensitive to the
empirical prior, decreasing by 56\%.
By using the empirically informed prior, we ignored prior uncertainty, leading
to an underestimate of our posterior uncertainty (Figure~\ref{figCoinFlip}).
While this did not greatly affect our estimate of \myTheta{}, it did mislead us
toward overconfidence in Model 2.
% Our mode estimate of \myTheta{} under the empirical prior might be closer
% to the true value than our posterior mode.
% Let us assume the truth of the matter is that the coin under study has a broad
% flat edge, and as a result lands on its edge at a certain frequency.
% Hence, both of our models are incorrect (i.e., the outcomes of flipping the
% coin are not binomially distributed).

@@

% \cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes
%     approaches for model choice when using uniform priors can exclude the
%     $truth$ from the prior, which is a violation of Bayes theorem" or something
%     like that. Picking apart what they calculated and we calculated seems like
%     too much detail. I would try to simplify how this is being presented. This
%     can lead into how the use of more appropriate prior distributions should be
%     used.}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors for a method
that has already been shown to be biased toward models with less parameter
space.
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
many of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
Thus, the results of \citet{Hickerson2013} indicate that integration over
parameter space with low likelihood is biasing the method toward models with
smaller parameter space, and as a consequence is biasing the method toward
models that exclude the truth (i.e., toward estimating model-averaged
posteriors dominated by models that exclude true values of parameters of the
model).

@@

There was an error in the methods of \citet{Hickerson2013} resulting in
an erroneous model that mixes different units of time (see SI for
details).
For our re-analysis of the Philippines dataset we followed the model-averaging
approach of \citet{Hickerson2013}, but with a reduced set of prior models to
avoid the error.
We used five prior models, all of which had priors on population sizes of
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these models had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
We simulated $1\e6$ random samples from each of the models for a total of
$5\e6$ prior samples.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
From the remaining 50,000 samples, we then retained the 10,000 samples with the
smallest Euclidean distance from the observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
We then repeated this analysis twice, replacing the $M_1$ with
$M_{1A}$ and $M_{1B}$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of at least
some of the 22 taxa, we are nearly certain that these narrower priors are
incorrect and exclude most, if not all, of the divergence times of the
Philippine taxa.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's bias toward models with less parameter space,
but rather allows it to manifest in a rather dangerous way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).

\citet{Hickerson2013} vetted the priors used in their model-averaging approach
via ``graphical checks,'' in which the summary statistics from 1000 random
samples of each prior model are plotted along the first two orthogonal axes of
a principle component analysis (see Figure 1 of \citet{Hickerson2013}).
To determine if such prior predictive analyses would indicate the $M_{1A}$ and
$M_{1B}$ are are problematic, we performed these graphical checks on our prior
models.
Unfortunately, these prior predictive checks provide no warning that these
priors are too narrow (Figure~S\ref{figPCA}).
Rather, they suggest these incorrect priors are ``better fit''
(Figure~S\ref{figPCA}A--C) than the valid priors similar to those used by
\citet{Oaks2012} (Figure~S\ref{figPCA}D--F).

Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret
(in addition to the error of time units).

@@

Contrary to Hickerson et al.'s (\citeyear{Hickerson2013}) claim that their
model-averaging approach ``can discriminate complex multispecies histories and
correctly reject synchronous divergence, even when discrete divergence times
differ by much less than \ldots millions of generations,'' our results show
that method is biased toward supporting the extreme case of a single
divergence event when populations diverged randomly over the last
$8\globalpopsize$ generations.
To put this on the scale roughly consistent with a vertebrate mitochondrial
locus, assuming a mutation rate of $2\e{-8}$ per site per generation, this
translates to 5 million generations.
Assuming a mutation rate consistent with nuclear loci of $1\e{-9}$, this is 100
million generations.

>>>>

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    are affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citep{Huang2011} introduced an approximate Bayesian approach which can be
    used to estimate the probability of a model in which multiple sets of taxa
    diverge at the same time. 
    This method (implemented in the software \msb) does not require a common
    set of character data that links all of the taxa under investigation, but
    does require the relative mutation rates among the taxa and loci to be
    assumed a priori.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the 
    prior that is chosen and that the inference method had low power
    to detect variation in divergences times.
    These results were not surprising, in light of a rich statistical literature
    that shows that the marginal likelihood of a model is quite sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors and the method's ability to detect
    temporal variation in divergences.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically informed uniform
    priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an 
    empirical Bayesian stance for this model-choice problem.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes}

@@

\citet{Oaks2012} suggest the primary cause of the spurious support for models
with few divergence parameters is the greater marginal likelihoods of these
models under vague uniform priors relative to more parameter-rich models.
Models with more divergence-time parameters integrate over \emph{much} greater
parameter space with low probability of producing the data, yet relatively high
prior density \citep{Lindley1957} imposed by the uniformly distributed prior on
divergence times.
Note, this is a statistical issue extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is the result of a numerical issue
intrinsic to \msb, concluding the method's rejection algorithm is inefficient
and will be biased toward models with fewer divergence-time parameters, because
the parameter space of these models are more densely sampled relative to models
with more divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results of additional analyses that, when combined with
the results of \citet{Oaks2012}, strongly suggest small marginal likelihoods of
models with more parameter space is a primary mechanism by which uniform priors
are causing \msb to prefer highly clustered models of divergences.

@@

% There are also differences between the papers regarding potential solutions to
% the bias.
\citet{Oaks2012} suggest alternative prior probability distributions on
divergence-times and other nuisance parameters could increase the marginal
likelihoods of models with more divergence-time parameters and thus reduce the
bias.
Alternatively, \citet{Hickerson2013} present an approach that uses empirically
informed uniform priors and Bayesian model-averaging in an attempt to accommodate
uncertainty in selecting priors.
% \citet{Hickerson2013} champion this strategy as a means of avoiding the
% pitfalls raised by \citet{Oaks2012}.
In general, we agree with the use of Bayesian model averaging to obtain a
posterior estimate marginalized over uncertainty in prior choice.
However, we question whether adding an additional dimension of model choice
that samples over empirically informed uniform priors is a fruitful solution
for a model-choice method that is very sensitive to priors.

In this paper, we discuss the potential theoretical and practical problems of
using empirically informed priors for Bayesian model choice.
Furthermore, we evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different multiple units of time, which makes the
results presented in their response difficult to interpret (see Supporting
Information for details).
Even when avoiding this error, we find Hickerson et al.'s
\citeyear{Hickerson2013} empirical Bayesian model-averaging implementation of
\msb remains biased toward clustered divergence models, and is predisposed to
excluding true parameter space.
The approach provides another means by which the method can ``escape'' models
with large parameter space, and the method's bias toward smaller models
remains.
Importantly, this bias can manifest in the preference of models that exclude
from consideration the true values of the model's parameters.
Our results, when combined with those of \citet{Oaks2012}, suggest that it is
difficult to choose a uniformly distributed prior on divergence times that is
broad enough to confidently contain the true values of parameters while being
narrow enough to avoid bias toward models with less parameter space.
However, recent work shows altnerative probability distributions without a
hard upper bound (e.g. gamma) can accomodate prior uncertainty in divergence
times while increasing the method's power to detect temporal variation in
divergences
\citet{Oaks2014dpp}.

@@

\citet{Hickerson2013} suggest that \citet{Oaks2012} should have used their
data to inform their prior on divergence times (i.e., an empirical Bayesian
approach).
However, \citet{Oaks2012} did use empirically informed priors to mimic
empirical situations in which a large amount of prior information is available;
they did so to assess the prior sensitivity of the method and to determine if
uniform priors in such situations are narrow enough to avoid the bias toward
models with few divergence-time parameters.
The results of \citet{Oaks2012} and \citet{Hickerson2013} showed the method is
highly sensitive to the prior on divergence times.
Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
divergences even under the informed priors.

@@

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a method of inductive learning in which Bayes' rule is
used to update our beliefs about a model $M$ as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values for model $M$, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta \given M)$ describes our belief that
any given \myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta, M)$ measures our belief that any dataset \alignment{}{}
will be generated by any state \myTheta{} of model $M$.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}, M) = \frac{p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M)}{p(\alignment{i}{} \given M)},
    \label{eq:bayesrule}
\end{equation}
as a measure of our beliefs after seeing the new information, where
\begin{equation}
    p(\alignment{i}{} \given M) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M) d\myTheta{}
    \label{eq:marginallikelhiood}
\end{equation}
is the marginal likelihood of the model.
\end{linenomath}

@@

Thus, empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and incorrectly shaped;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
This is not to say that empirical Bayesian approaches are not useful.
Empirical Bayes is a well-studied branch of Bayesian statistics that has given
rise to many inference methods that provide means of parameter estimation that
often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

@@

Another important difference of Bayesian model choice illustrated by
Equation~\ref{eq:bayesmodelchoice} is that the value of interest, the
posterior probability of a model, is not a function of \myTheta{}, because
it is integrated out of the marginal likelihoods of the candidate models.
Thus, unlike parameter estimates, the estimated posterior probability of a
model is a single value (rather than a distribution) lacking a measure of
posterior uncertainty.
Also, unlike model parameters, the posterior probabilities of candidate
models have no clear true values.
% In some simple situations we might suspect that one model is correct and the
% rest are wrong, but in most applications, we know that all the models under
% consideration are oversimplifications of reality.
Model posterior probabilities are inherently measures of our belief in the
models after our prior beliefs are updated by the data being analyzed.

@@

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the fairness of a particular coin, and we
denote the unknown probability of it landing heads as \myTheta{}.
More specifically, we are interested in the probability of two models, $M_1$
and $M_2$.
In both models the outcomes of flipping the coin are assumed to be binomially
distributed, but under $M_1$ the coin is weighted toward landing heads (i.e.,
$\myTheta{} > 0.5)$), whereas under $M_2$, the coin is weighted toward landing
tails (i.e., $\myTheta{} < 0.5$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times, and so we decide to use these data in specifying a
beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin $N=10$ times, $y=3$ of which land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$
(Figure~\ref{figCoinFlip}).
The maximum a posteriori (MAP) estimate of the probability of heads is 0.429,
and following Equation~\ref{eq:marginallikelhiood} the marginal likelihoods of
our models of interest are
\begin{equation}
    p(y=3, N=10 \given M_1) = \int_{0.5}^{1} p(y=3, N=10 \given
    \myTheta{}, M_1)p(\myTheta{} \given M_1) d\myTheta{} \approx 0.029,
\end{equation}
and
\begin{equation}
    p(y=3, N=10 \given M_2) = \int_{0}^{0.5} p(y=3, N=10 \given
    \myTheta{}, M_2)p(\myTheta{} \given M_2) d\myTheta{} \approx 0.097.
\end{equation}
Given the models have equal probability under our prior, we can calculate the
posterior probability of Model 1 as
\begin{equation}
    p(M_1 \given y=3, N=10) = \frac{p(y=3, N=10 \given M_1)}{p(y=3, N=10 \given
    M_1) + p(y=3, N=10 \given M_2)} \approx 0.23.
\end{equation}
This is the correct posterior probability of Model 1 given our prior
and data.

To give the data more weight relative to the prior, we could use it twice, and
calculate an empirical Bayes estimate using a prior of $beta(13,17)$.  This
results in a ``posterior'' distribution of $beta(16, 24)$
(Figure~\ref{figCoinFlip}), with a MAP estimate of 0.395, and $p(M_1 \given
y=3, N=10) = 0.10$.
The estimated posterior distribution of the parameter, and resulting MAP
estimate, is similar whether or not an empirically informed prior is used.
However, the posterior probability of Model 1 is very sensitive to the
empirical prior, decreasing by 56\%.
By using the empirically informed prior, we ignored prior uncertainty, leading
to an underestimate of our posterior uncertainty (Figure~\ref{figCoinFlip}).
While this did not greatly affect our estimate of \myTheta{}, it did mislead us
toward overconfidence in Model 2.
% Our mode estimate of \myTheta{} under the empirical prior might be closer
% to the true value than our posterior mode.
% Let us assume the truth of the matter is that the coin under study has a broad
% flat edge, and as a result lands on its edge at a certain frequency.
% Hence, both of our models are incorrect (i.e., the outcomes of flipping the
% coin are not binomially distributed).

@@

% \cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes
%     approaches for model choice when using uniform priors can exclude the
%     $truth$ from the prior, which is a violation of Bayes theorem" or something
%     like that. Picking apart what they calculated and we calculated seems like
%     too much detail. I would try to simplify how this is being presented. This
%     can lead into how the use of more appropriate prior distributions should be
%     used.}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors for a method
that has already been shown to be biased toward models with less parameter
space.
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
many of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
The strong preference for the questionable priors on divergence times (their
$M_1$ and $M_2$) in the model-averaged results of \citet{Hickerson2013} suggest
their approach is biased toward models with less parameter space, and as a
consequence, is biased toward models that likely exclude the truth.
I.e., the approach is biased toward estimating model-averaged posteriors
dominated by models that exclude true values of parameters of the model.

@@

For our re-analysis of the Philippines dataset we followed the model-averaging
approach of \citet{Hickerson2013}, but with a reduced set of prior models to
avoid their error of mixing units of time (see SI for details).
We used five prior models, all of which had priors on population sizes of
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these models had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
We simulated $1\e6$ random samples from each of the models for a total of
$5\e6$ prior samples.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
From the remaining 50,000 samples, we then retained the 10,000 samples with the
smallest Euclidean distance from the observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
We then repeated this analysis twice, replacing the $M_1$ model with
$M_{1A}$ and $M_{1B}$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of at least
some of the 22 taxa, we are nearly certain that these narrower priors are
incorrect and exclude most, if not all, of the divergence times of the
Philippine taxa.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's bias toward models with less parameter space,
but rather allows it to manifest in a concerning way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).

However, \citet{Hickerson2013} vetted the priors used in their model-averaging
approach via ``graphical checks,'' in which the summary statistics from 1000
random samples of each prior model are plotted along the first two orthogonal
axes of a principle component analysis (see Figure 1 of \citet{Hickerson2013}).
To determine if such prior predictive analyses would indicate the $M_{1A}$ and
$M_{1B}$ models are problematic, we performed these graphical checks on our
prior models.
Unfortunately, these prior predictive checks provide no warning that these
priors are too narrow (Figure~S\ref{figPCA}).
Rather, the graphs suggest these incorrect priors are ``better fit''
(Figure~S\ref{figPCA}A--C) than the valid priors similar to those used by
\citet{Oaks2012} (Figure~S\ref{figPCA}D--F).

Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret.

@@

Our results show that the empirical Baysian model-averaging approach is biased
toward supporting the extreme case of a single divergence event when
populations diverged randomly over the last $8\globalpopsize$ generations.
To put this on the scale roughly consistent with a vertebrate mitochondrial
locus, assuming a mutation rate of $2\e{-8}$ per site per generation, this
translates to 5 million generations.
Assuming a mutation rate consistent with nuclear loci of $1\e{-9}$, this is 100
million generations.
